### 2016-12-19 local-capability-machine.tex
updated name of observations anti reduction lemma
Comment for enter cap. Should they be global/local after jump?

@@

\begin{lemma}[Execution and $\observations$]
  \begin{align*}
    & \forall n,i,\reg, \reg', \ms, \ms', \ms_r, W \ldotp\\
    & \quad (\forall \ms_f \ldotp (\reg,\ms \uplus \ms_r \uplus \ms_f) \step[i] (\reg',\ms' \uplus \ms_r \uplus \ms_f)) \land \npair[n-i]{(\reg',\ms')} \in \observations(W) \\
    & \qquad \Rightarrow \npair{(\reg,\ms \uplus \ms_r)} \in \observations(W)
  \end{align*}

>>>>

\lau{At some point we talked about whether $\updatePcPerm{}$ should just give a $\glob$ capability all the time. I believe this is dangerous as it can be used to first get a $\glob$ read-capability for the stack and subsequently in a $\glob$ callback, you can start reading from someone elses private stack!}

@@

\begin{lemma}[Anti-reduction for $\observations$]
  \begin{align*}
    & \forall n,i,\reg, \reg', \ms, \ms', \ms_r, W \ldotp\\
    & \quad (\forall \ms_f \ldotp (\reg,\ms \uplus \ms_r \uplus \ms_f) \step[i] (\reg',\ms' \uplus \ms_r \uplus \ms_f)) \land \npair[n-i]{(\reg',\ms')} \in \observations(W) \\
    & \qquad \Rightarrow \npair{(\reg,\ms \uplus \ms_r)} \in \observations(W)
  \end{align*}
